Analyzing Build Logs Using Programming by Example

### 2019-06-25 paper/paper.tex
fix paper typos & compilation errors

\plan{why are logs so difficult: mention heterogenous, semi-structured (paper reference for that?), big data (refercene paper about log sizes), in distributed systems probably distributed (really also for buildlog?)

to combat that useres write tools to <extract / rerieve superbegriff> information from buildlogs.

one possibility IR: classfy specifict part of program as similar to others (list IR technique) to see whether it is correclated to a failure. but not as good: not a real summarization technique, more what is similar to the last few times it faied.

@@

MAYBE IN THE other paragraph. here only half fitting?
}

@@

\draft{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix. On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
Instead of recieving a paragraph which is similar to a givien query, our works focus more on obtaining specific pieces of texts through regular expressions.

>>>>

\plan{why are logs so difficult: mention heterogeneous, semi-structured (paper reference for that?), big data (reference paper about log sizes), in distributed systems probably distributed (really also for build log?)

to combat that users write tools to <extract / retrieve superbegriff> information from build logs.

one possibility IR: classify specific part of program as similar to others (list IR technique) to see whether it is correlated to a failure. but not as good: not a real summarization technique, more what is similar to the last few times it failed.

@@

\todo{maybe other paragraph. here only half fitting?}
}

@@

\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix. On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}
